---
title: "Things you did not know about the Olympic Games"
author: "Daniel Escoval"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: paged
    code_fold: hide
    toc: true
editor_options: 
  markdown: 
    wrap: sentence
---
```{r message=FALSE, warning=FALSE, echo=FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(plotly)
library(viridis)
library(infer)
library(stringr)
```


# Introduction

In this report we will get some analysis about the Olympic Games and what data can tell us about the Olympic Games and their history.

# The data
```{r, echo=FALSE}
athletes_tibble <- read_xlsx("olympics.xlsx", sheet = "athletes") %>%
  mutate(ID = as.character(ID)) %>%
  rename(c(athlete_id=ID))
countries_tibble <- read_xlsx("olympics.xlsx", sheet = "country") %>%
  mutate(athlete_id = as.character(athlete_id))
games_tibble <- read_xlsx("olympics.xlsx", sheet = "games")
medals_tibble <- read_xlsx("olympics.xlsx", sheet = "medals") %>%
  mutate(athlete_id = as.character(athlete_id))
```

The data is in a big Excel file with 4 sheets.

* The first sheet focuses on athletes and their characteristics.
```{r} 
glimpse(athletes_tibble)
```

* The second sheet shows the NOCs (National Olympic Committees) who participated to an Event.
  It means we should expect a lot of duplicates.
```{r}
glimpse(countries_tibble)
```

* The third sheet is also the smallest dataset focuses on the each Olympic Games characteristic.
```{r}
glimpse(games_tibble)
```

* The fourth sheet focuses on who won a medal. This dataset is the biggest one as there is 1 row per athlete, per event per Games. It means if 4 individuals won a Gold medal during an event, them the country will earn 4 medals.
```{r}
glimpse(medals_tibble)
```

## Analysis

### Athletes analysis

Have some athletes competed for different countries over time?
```{r}
#Join athletes and country table
athletes_country <-  merge(x=athletes_tibble,y=countries_tibble, by="athlete_id")


athletes_country_numbers <- athletes_country %>%
  distinct(athlete_id, NOC, .keep_all = TRUE) %>%
  group_by(athlete_id) %>%
  summarise(countries = list(NOC)) %>%
  ungroup %>%
  mutate(nb_countries = lengths(countries)) %>%
  group_by(nb_countries) %>%
  summarise(nb_athletes_by_country = n()) %>%
  ungroup

filtered_athletes_country_numbers <- athletes_country_numbers %>%
  filter(nb_countries > 1) %>%
  summarise(more_1_country = sum(nb_athletes_by_country))

filtered_athletes_country_numbers

```
Yes, `r filtered_athletes_country_numbers` athletes have competed for 2 or more countries.

We can find more details in the plot below:

```{r}
athletes_country_numbers %>%
  ggplot(aes(x = fct_reorder(as.character(nb_countries), nb_athletes_by_country), y = nb_athletes_by_country)) +
  geom_col(width = 0.7) +
  coord_flip()+
  labs(
    title="Number of athletes per number of coutries reprentation",
    x="Number of coutries represented by the an athlete",
    y="Number of athletes"
    )
```
Indeed, we see that the massive number of athletes only competed for one country, but it can be interesting to zoom in the `r filtered_athletes_country_numbers` athletes who competed for more than one country.
```{r}
p <-athletes_country_numbers %>%
  filter(nb_countries > 1) %>%
  # prepare text for tooltip
  mutate(text = paste("Number of athletes in this group: ", nb_athletes_by_country)) %>%
  
  ggplot(aes(x = nb_countries, y = nb_athletes_by_country, text=text)) +
  geom_point(alpha=0.7) +
  scale_size(range = c(1.4, 10), name="Number of athletes") +
  scale_color_viridis(discrete=TRUE, guide=FALSE) +
  theme(legend.position="none")+
  labs(
    title="Number of athletes per number of coutries reprentation",
    x="Number of coutries represented by the an athlete",
    y="Number of athletes"
    )
  
# turn ggplot interactive with plotly
pp <- ggplotly(p, tooltip="text")
pp
```

This is expected that athletes compete for more than one country for various reasons:

* The athlete changed his country for personnal reasons.
* The country does not exist any more (you can find here an example of countries that disappeared after World War 2: https://landgeist.com/2021/05/25/countries-that-ceased-to-exist-since-ww2/)
* The country changed its name (https://www.jagranjosh.com/general-knowledge/countries-that-changed-their-names-1694008654-1)
* Remember that we are not really talking about "countries" but about NOCs, in the case of Russia, after the Winter Games of 2018 in Pyeongchang, Russian athletes cannot represent Russia Barrymore, but ROC (Russian Olympic Committee).
* Also the IOC code for the NOC can change, a scenario that can also appear in our data.
* The athlete competes for the EOR (European Reffugee Team)

Let's take the example of the five athletes who represented 4 countries during the Olympic Games history:

```{r}
athletes_country %>%
  distinct(athlete_id, NOC, .keep_all = TRUE) %>%
  group_by(athlete_id) %>%
  reframe(Name, countries = list(NOC), list_games = list(Games)) %>%
  ungroup %>%
  distinct(Name, .keep_all = TRUE) %>%
  mutate(nb_countries = lengths(countries)) %>%
  filter(nb_countries == 4) %>%
  unnest(countries, list_games) %>%
  select(-c(athlete_id, nb_countries))
```

We can see that all of them were in at least a country that does not exist any more for their first Games.

Now that we have the athletes and which country they represented, we can ask ourselves who are the ten athletes that took part in most games?

```{r}
athletes_country %>%
  group_by(athlete_id) %>%
  reframe(number_participation = n(), Name) %>%
  distinct(Name, .keep_all = TRUE) %>%
  arrange(desc(number_participation)) %>%
  head(12) %>%
  ungroup
```
It is difficult to give a top 10 as 9 athletes participated at 8 iterations of the games, 2 at 9 iterations and 1, Ian Millar at 10 iterations.

This is not very surprising as he's an equestrian and equestrian athletes are the ones who can have the longest career. The 2 other athletes with 8 participations are a shooter and a sailor, who also have long careers. 

Now we know who are the athletes who participated in most Games, let's see if they also are the ones who competed in the most events?
If they are not in the top ten, who are in there?
Also, did some athletes take part in more than one event during a game?

```{r}
athletes_medals <-  merge(x=athletes_tibble,y=medals_tibble, by="athlete_id")

athletes_medals %>%
  group_by(athlete_id, Games) %>%
  reframe(events_per_games = n(), Name, Event) %>%
  distinct(Name, .keep_all = TRUE) %>%
  arrange(desc(events_per_games)) %>%
  head(10)
```
Acee Blue Eagle is the person who participated at the most events in our iteration of Olympic Games. It is interesting to see that they were all artists or shooters.

### Medals analysis
Now let's focus on countries and how many medals they won.

LEt's create a new table showing the number of medals per country (rows) and per year (column).
Keep only the 15 countries with the most medals overall.

```{r}
athletes_medals_countries <- merge(x=athletes_medals,y=countries_tibble, by="athlete_id") %>%
  select(-Games.y) %>%
  rename(Games = Games.x)

top_15_countries <- athletes_medals_countries %>%
  drop_na(Medal) %>%
  group_by(NOC) %>%
  mutate(total_medals = n()) %>%
  ungroup() %>%
  arrange(desc(total_medals)) %>%
  distinct(NOC, pick(total_medals)) %>%
  head(15)

top_15_countries_vector <- top_15_countries$NOC

top_countries_games <- merge(x=top_15_countries,y=athletes_medals_countries, by="NOC")

top_countries_games %>%
  group_by(NOC, Games) %>%
  reframe(medal_by_envent = n(), total_medals) %>%
  ungroup() %>%
  arrange(desc(total_medals)) %>%
  distinct(total_medals,Games,NOC, .keep_all = TRUE) %>%
  pivot_wider(
    names_from = "Games",
    values_from = medal_by_envent
  )
  
```
This final table has very interesting data on it.
First, we can see that by far USA is the country with the biggest number of medals overall, with 9859 medals.
The top 3 is completed by Germany and URSS, which is the only country that does not exist any more now.

The story of URSS is very interesting. Indeed the Union of Soviet Socialist Republics was officially created in 1922 and disappeared end of 1991. So, this country was not able to compete in the first Olympic Games and in the the ones from 1992, but we see that it "earns" some medals after 1992, meaning an athlete who previously represented URSS still competed under another flag and hour data does not show us which flag. Without too much difficulty, we can say that the country inheriting from URSS is directly Russia who began to win a significant number of medals directly in 1992. Like the URSS, we can still see some athlete medals before its creation, it's due to some small issues in the way data is counted.
To show the USA supreme in sport, even URSS + Russia does 7392 medals, which means that USA is still ahead of 2467 medals in total.

Is there a relationship between country and the probability of winning a medal?

We know that some countries win more medals than others.
In this part we want to work out whether some countries win more medals simply because they have more athletes competing for more events, or whether their athletes are in fact performing better in general.

For this part, look only at the top 15 countries that you established in part 4.

- Create a horizontal barchart listing for each of the fifteen countries the percentage of medals won *out of all medals competed for by that country*. 

```{r}
medals_per_athletes_nb <- athletes_medals_countries %>%
  distinct(athlete_id, .keep_all = TRUE) %>%
  select(athlete_id, Games, Event, Medal, NOC) %>%
  replace_na(list(Medal = "No Medal")) %>%
  group_by(NOC) %>%
  mutate(athletes_per_country = n()) %>%
  ungroup() %>%
  group_by(Medal, NOC) %>%
  mutate(won_by_medal = n()) %>%
  ungroup() %>%
  mutate(percentage = won_by_medal/athletes_per_country) %>%
  mutate(percentage = percentage*100)

medals_per_athletes_nb %>%
  filter(NOC %in% top_15_countries_vector) %>%
  ggplot(aes(x=Medal, y=percentage)) + 
  geom_bar(stat="identity") +
  facet_wrap(vars(NOC))+
  coord_flip() + 
  labs(
    title="Percentage of medal won by a country",
    x="Type of medal",
    y="Percentage of wins"
    )
```
- Looking at the chart, what do you think: is there a relationship between country and the probability of winning a medal? Comment your findings.
Well, it seems that not winning a medal stays the norm. What we see is that USA has the biggest columns for everything, meaning more you have athletes, more you have chances to earn a medal, in the opposit, URSS has the smallest "No Medal" column, but the other columns a very visible, meaning that an URSS athlete had more chances to win a Medal overall.

- Run a Chi Square test to test the null-hypothesis: "There is no relationship between country and whether they win a medal or not".

```{r}
medals_per_athletes_nb %>%
  chisq_test(
    formula = Medal ~ NOC
    )

```
It seems, indeed that there is a very strong association between winning a medal and the NOC.
The p_value is 0, meaning that there is a strong evidence we can refuse the null hypothesis.

### Some sport analysis
Create a scatterplot showing the average height versus the average weight of competitors per sport (one dot per sport).

```{r}
sport_averages <- athletes_medals_countries %>%
  distinct(athlete_id, .keep_all = TRUE) %>%
  drop_na(Height) %>%
  drop_na(Weight) %>%
  group_by(Sport) %>%
  summarise(
    mean_weight = mean(Weight),
    mean_height = mean(Height),
    mean_bmi = mean_weight / ((mean_height/100))^2
    )
sport_averages

extreme_value <- sport_averages %>%
  summarise(
    max_weight = max(mean_weight),
    min_weight = min(mean_weight),
    max_height = max(mean_height),
    min_height = min(mean_height),
    max_bmi = max(mean_bmi),
    min_bmi = min(mean_bmi)
  )

```

```{r}
extreme_value
```

```{r}
sport_averages %>%
  ggplot(aes(x=mean_weight, y=mean_height, label=Sport))+
  geom_point() +
  geom_point(
    data = sport_averages %>%
      filter(
        mean_weight == max(mean_weight) | mean_weight == min(mean_weight) |
          mean_height == max(mean_height) | mean_height == min(mean_height) |
          mean_bmi == max(mean_bmi) | mean_bmi == min(mean_bmi)
             ),
    colour = "red"
    )+
  geom_text(
    data = sport_averages %>%
      filter(
        mean_weight == max(mean_weight) | mean_weight == min(mean_weight) |
          mean_height == max(mean_height) | mean_height == min(mean_height) |
          mean_bmi == max(mean_bmi) | mean_bmi == min(mean_bmi)
             ),
    check_overlap = TRUE,
    size = 2,
    hjust = 0.3,
    nudge_x = 0.2,
    vjust = 0, 
    nudge_y = -1.2
    ) +
  labs(
    title="Sports with extreme values",
    caption= "The sports in red are the sports with the minimal or maximal values.",
    x="Mean height",
    y="Mean weight"
    )

```
### Part 7

Create a line plot showing the number of medals given by year (one line for Gold, one line for Silver and one line for Bronze).
Does it change over time?
Use facets to separate the medals at Summer games and Winter games.

Comment the results below the plot.
```{r}
medals_tibble %>%
  distinct(Games, Event, .keep_all = TRUE) %>%
  select(Games, Sport, Medal) %>%
  mutate(year =  as.numeric(str_extract(Games, regex("\\d+")))) %>%
  mutate(season = str_extract(Games, regex("([A-Z])\\w+"))) %>%
  drop_na(Medal) %>%
  group_by(Medal,year, season) %>%
  summarise(
    medals_per_year = n()) %>%
  ggplot(aes(x=year, y=medals_per_year, group=Medal, color=Medal)) +
  geom_line() +
  facet_wrap(vars(season)) +
  labs(
    title="Medals distribution over time",
    x="Years",
    y="Number of medals distributed"
    )
```
The first thing that comes to the eye is the different between the Winter and Summer sports.
As Winter has historically less sports, it is normal to see less medals.

I also was expecting to see the same number of Bronze, Silver and Gold medal, instead, we can see that the lines are never superposed, which means there is never the same number of Bronze, Silver and Gold medals distributed in an event.

#Conclusion
The Olympic Games evolved a lot during their history.They followed the world and its changes, with more or less countries, wwith different disciplines and so on.

# Sources
## Help for coding
https://r-graph-gallery.com/bubble_chart_interactive_ggplotly.html

## Help for analysis
https://en.wikipedia.org/wiki/Ian_Millar
https://en.wikipedia.org/wiki/Acee_Blue_Eagle
